---
title: "UsingRstudioWithGit"
author: "RUI. GUO"
date: '2023-10-27'
output: html_document
---
## 1 Install Git
### Confirm that you installed Git correctly
git --version # run this in the terminal
---
git version 2.33.0
---

## 2 Configure Git
### Install package
```{r pkg install}
install.packages("usethis")
```

### Tell Git who we are
```{r config}
#### Use the edit_git_config() function from the usethis package, which will open your gitconfig file. Add your name and email and close this.

library(usethis)
use_git_config(user.name = "LaneyGUO", user.email = "laneyguo5@163.com")

```

### Initialize a Git Repository
```{r}
### The use_git() function will add a Git repository (often referred to as a “repo”) to an existing RStudio project

library(usethis)
use_git()

### Then choose and input your selection in console to finish initialize
```


## 3 View Commit History

```{r}
### Now that my RStudio project has an associated Git repository, I'll see an extra tab on the top right: the Git tab. From here, I can see the entire history of changes to my code over time (not many yet!).
```

### Make a Commit and View More History
---
RStudio has a built-in tool to view your code history. You can click on any commit to see what changed, relative to the previous commit. Lines in green were added; lines in red were deleted.
---
```{r}
library(tidyverse)
```


## 4 Connect RStudio and GitHub

### Sign up for Github

### Create a Personal Access Token (PAT) on GitHub
---
The best way to connect RStudio and GitHub is using your username and a Personal Access Token (PAT).

To generate a personal access token, use the create_github_token() function from usethis. This will take you to the appropriate page on the GitHub website, where you’ll give your token a name and copy it (don’t lose it because it will never appear again!).
---
```{r}
library(usethis)
create_github_token()
## 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
```

### Store Personal Access Token to Connect RStudio and GitHub
---
Now that you’ve created a Personal Access Token, we need to store it so that RStudio can access it and know to connect to your GitHub account.

The gitcreds_set() function from the gitcreds package will help you here. You’ll enter your GitHub username and the Personal Access Token as your password
---
```{r}
library(gitcreds)
gitcreds_set()
```

